
\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\namesection{}{Shreyas Singh}{ \urlstyle{same}\url{} 
\href{mailto:shraeyassingh@gmail.com}{shraeyassingh@gmail.com} | +91 9455069397
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{IET, Lucknow}
\descript{B.Tech. in Information Technology}
\location{Expected 2019 | Lucknow, IN \\ Percentage : 71.13}
\sectionsep


\descript{The Avadh School}
\location{2014 | Lucknow, IN}
Class XIIth \\
PCM \\
\location{ Percentage : 85.4}
\sectionsep

\descript{St. Anthony Sr. Sec. School}
\location{2012 | Barabanki, IN}
Class Xth \\
\location{ CGPA : 9.6}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/Shraeyas}{\custombold{Shraeyas}} \\
LinkedIn://  \href{https://www.linkedin.com/in/shraeyas}{\custombold{Shraeyas}} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}

\descript{Undergraduate}
\textbullet{} Operating Systems \\
\textbullet{} Data Structures and Algorithms \\
\textbullet{} Computer Networks \\
\sectionsep
\descript{Higher Sec. School}
\textbullet{} C, C++
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\location{Programming Languages}
\textbullet{} Java\\
\textbullet{} Python\\
\textbullet{} JavaScript\\
\textbullet{} C\\
\textbullet{} C++\\
\textbullet{} CSS\\
\textbullet{} HTML\\
\textbullet{} PHP\\
\sectionsep
\location{Familiar }
\textbullet{} Android Studio\\
\textbullet{} MySQL\\
\textbullet{} OOP\\
\textbullet{} PHP Slim Framework\\
\textbullet{} REST APIs\\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     INTERESTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Interests}
\textbullet{} Competitive Programming\\
\textbullet{} Web Development\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Balloon (Social Network Startup)}
\descript{| Android Development Intern | June 2018 – July 2018}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Developed and released the beta version for the Android App.
\item Designed the entire UI for the app and connected the app with the backend REST API using the Volley and OKHttp libraries in Java.
\end{tightemize}
\sectionsep

\runsubsection{Carebunny Health Care (Medical E-commerce startup)}
\descript{| Web Development Intern (PHP, MySQL) | Jan 2018 – Feb 2018}
\begin{tightemize}
\item Worked on creating a backend similar to the magento marketplace.
\item Implemented functionalities for allowing vendors to add/modify a product and have varying discount prices for different product quantities.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS/HACKATHONS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects/Hackathons}
\href{https://databread.xyz}{\runsubsection{Databread}}
\descript{| Founder | March 2017 – Present}
Developed a \textbf{\href{https://databread.xyz/}{website}} to fetch and display rating from Competitive Programming websites at one place. Used PHP, MySQL for backend and HTML, CSS, Bootstrap for frontend. It has 400+ users from across the globe.

\sectionsep

\href{https://github.com/Shraeyas/Drone-Image-Stitching}{\runsubsection{Drone Captured Image Stitching}}
\descript{| Tata Innoverse Hackathon | April 2017}
Built using Python, a software to stitch together images captured by a drone. I participated in a team of 2 where my responsibility included writing script for extracting the geo-Exif data from the images and using an image compression library to make the whole process faster.

\sectionsep

\href{https://github.com/Shraeyas/IP-Camera-Intrusion-Detection}{\runsubsection{Intrusion Detection using Facial Recognition}}
\descript{| Academic Project (B.Tech 3rd Year) | January 2018}
Built using Python, it takes camera feed as input and can register the recognised faces within to a database which can be used as an intrusion detection system for surveillance cameras. The face recognition module was forked from \textbf{\href{https://github.com/ageitgey/face_recognition}{this github user.}}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Mini/Hobby Projects
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Hobby Projects}
\href{https://cat.databread.xyz/}{\runsubsection{Codechef Attendance Tool}}\\
Built a website where a user can view their attendance in various contests held on \textbf{\href{https://codechef.com}{Codechef}} and has over 3000+ visits.

\sectionsep

\href{https://crp.databread.xyz/}{\runsubsection{Codechef Rating Predictor}}\\
Developed a website which can predict user rating based on the performance in contests held on \textbf{\href{https://codechef.com}{Codechef.}}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     POSITIONS OF RESPONSIBILITIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Positions of Responsibility}

\runsubsection{Ciphertech}\\
Event Manager for Ciphertech, an Inter-College quiz contest with questions based upon deciphering a code. I also designed the web-based platform which was based upon PHP and MySQL for organising the event.

\end{minipage} 
\end{document}  \documentclass[]{article}